Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-15 presentations/bsa_2020-07-27/index.Rmd
Update slides

class: inverse, middle, title-slide, big-margin
background-color: #000000
background-position: 50% 50%
background-image: url(images/title_background.png)
background-size: contain

@@

```{r protected-areas, out.width = "120%", fig.asp = 0.65, fig.retina=200}
japan_box <- sf::st_bbox(ses_div_ferns_spatial)

>>>>

class: inverse, middle, title-slide, big-margin
background-color: #000000

@@

```{r protected-areas, out.width = "120%", fig.asp = 0.65, dev="png", dpi=200}
japan_box <- sf::st_bbox(ses_div_ferns_spatial)
